Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-01-25 reports/manuscript/sections/introduction.tex
Add Jason Yeatman's suggestions

independently at each node of each bundle, for each one of the
diffusion metrics available at that point. This approach is exhaustive, but

@@

\cite{huber2018rapid}). Sometimes, these approaches are combined: an

@@

The present work aims to balance predictive
accuracy with descriptive power \cite{Murdoch2019-ax, Breiman2001-uz}
by capitalizing on all of the data across all bundles, while also retaining and
elucidating spatial information about the locations that are most informative
for discriminative performance. To do so, we use a linear modeling approach,
which aims to redict phenotypical variance in a group of subjects, based on a
linear combination of the features estimated with tractometry.

>>>>

independently at each node of each bundle, for each
diffusion metric. This approach is exhaustive, but

@@

\cite{huber2018rapid}). Sometimes, these approaches are combined: a

@@

The present work aims to balance predictive accuracy with descriptive power
\cite{Murdoch2019-ax, Breiman2001-uz} by capitalizing on all of the available
data across all bundles, while also retaining and elucidating spatial
information about the locations that are most informative for discriminative
performance. To do so, we use a linear modeling approach, which aims to
redict phenotypical variance in a group of subjects (or classify group
membership), based on a linear combination of the features estimated with
tractometry.

### 2021-01-25 reports/manuscript/supplemental.tex
Fix internal cref to the SGL section in supplemental.tex
Add Jason Yeatman's suggestions

\title{Supplemental Material: Multidimensional analysis and detection of informative features in human white matter}

@@

Four different previously-published datasets were used here:

@@

\Cref{sec:sgl} describes a single SGL model. To further improve model
performance, we create ensemble models composed of $m = 20$ individual SGL
models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
Bagging relies on the underlying assumption that some of the error in a
single SGL model's prediction stems from a mismatch in the distributions of
training data used to fit the model and test data used to evaluate its
performance. To overcome this, bagging invokes the same base estimator (e.g.
SGL) many times with different training sets, which are created by sampling
the original training samples with replacement. The bagging meta-estimator's
prediction is then the average of its constituent estimators' predictions.
Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
regression coefficients $\hat{\beta}$, we are refering to these values
averaged over 20 estimators in the bagging meta-estimator.

>>>>

\title{Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter}

@@

Four different datasets were used here:

@@

The previous section describes a single SGL model. To further improve model
performance, we create ensemble models composed of $m = 20$ individual SGL
models using bootstrap aggregation (bagging) \cite{breiman1996bagging}.
Bagging relies on the underlying assumption that some of the error in a
single SGL model's prediction stems from a mismatch in the distributions of
training data used to fit the model and test data used to evaluate its
performance. To overcome this, bagging invokes the same base estimator (e.g.
SGL) many times with different training sets, which are created by sampling
the original training samples with replacement. The bagging meta-estimator's
prediction is then the average of its constituent estimators' predictions.
Likewise, when we report the hyperparameter values $\alpha$ and $\lambda$, or
regression coefficients $\hat{\beta}$, we are refering to these values
averaged over 20 estimators in the bagging meta-estimator.
